---
title: "R Notebook"
output: html_notebook
---

```{r setup}
#install.packages("NeuralNetTools")
#install.packages("zoo", dependencies = TRUE)
#install.packages("TSA")
#install.packages("timeDate")
#install.packages("TStools")


library('neuralnet')
  library('NeuralNetTools')
library(data.table)
library(beepr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(beepr)
library(magrittr)
library(TSA)
library(xts)
library(timeDate)
library(TStools)
```


wkds <- c( 'Mon', 'Tue', 'Wed' , 'Thu', 'Fri', 'Sat', 'Sun')
```{r import_format_data}

#import exchange and rename to friendly headings
#NOTE: there are empty days, presumeably where exchange was closed, saturday and sunday
exchange <- 
  read.csv("https://github.com/jaewilson07/Hello-World/raw/master/Datasets/DM%20and%20A/Exchange.csv") %>%
  rename( fxDate = YYYY.MM.DD, fxRate =  USD.EUR) %>%
  mutate(
    Wdy = factor(Wdy, levels = wkds, ordered = TRUE),
    fxDate = as.Date(fxDate, "%m/%d/%Y"),
    actRate = fxRate)
exchange <- setDT(exchange)


```

```{r format_timeSeries}
exchange_xts <- xts(exchange$fxRate, order.by = exchange$fxDate)


cbind(head(coredata(exchange_xts),20), head(index(exchange_xts),20))
attr(exchange_xts, 'frequency') <- 5

#set periodicity to weekly b/c decomposition does not work on daily.
exchange_xts_w <- to.weekly(exchange_xts)
#periodicity(exchange_xts)
#periodicity(exchange_xts_w)


```
```{r investigatetimeSeries}
exchange_lr <- lm(exchange_xts[,1] ~.index(exchange_xts))
plot(exchange_xts)
abline(exchange_lr)
#the data is NOT stationary because MEAN of points (lm) is shifting (there is an upward slope in the abline)
#our variance may not be equal because distance from mean line is not the same across intervals (periods)
#stationary data is required for many traditional time series analysis techniques


#monthly trend
plot(aggregate(exchange_xts[,1], month,  FUN=mean))

#annual trend ~ doesn't really make sense given that we don't have multiple full years of data
plot(aggregate(exchange_xts[,1], year,  FUN=mean))


```

```{r componentTS}
#Components of time series

#https://stackoverflow.com/questions/43175206/preserve-timestamp-after-decomposing-xts-in-r
#need function to convert xts object to ts object and back b/c decompose does not work with xts

decompose.xts <- function (x, type = c("additive", "multiplicative"), filter = NULL) {
  #the decompose function will break a timeseries into component parts (seasonal, trend, white noise)
  #type = if variance from mean (lm function) is steady versus multiplicative (wider swings in variance) as mean increases. 
  dts <- decompose(as.ts(x), type, filter)
    dts$x <- .xts(dts$x, .index(x))
    dts$seasonal <- .xts(dts$seasonal, .index(x))
    dts$trend <- .xts(dts$trend, .index(x))
    dts$random <- .xts(dts$random, .index(x))
    
    with(dts,
         structure(list(x = x, 
                        seasonal = seasonal, 
                        trend = trend,
                        random = if (type == "additive") x - seasonal - trend else x/seasonal/trend, 
                        class = "decomposed.xts")))
}

exchange_dc <- decompose.xts(exchange_xts, "multiplicative")


plot(exchange_xts)
abline(exchange_lr)
       
plot(log(exchange_xts))

plot(diff(log(exchange_xts)))
acf(diff(log(exchange_xts)))



```
